Correlation Clustering with Dynamic Super-Nodes (DySNCC)

### 2014-10-09 paper/egpaper_for_review.tex
paper

% Include other packages here, before hyperref.
\usepackage{my_macros}
\usepackage{paralist}
\usepackage{amsthm}
\usepackage{dirtytalk}
%\usepackage{framed}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{algpseudocode}
\usepackage{setspace}
%for tikz
\usepackage{tikz,pgfplots}
\usetikzlibrary{arrows,positioning,automata,shadows,fit,shapes}
\usetikzlibrary{arrows,petri,topaths}
\usetikzlibrary{positioning,fit,calc}
\usetikzlibrary{shapes.arrows,chains,decorations.pathreplacing,fadings}
\usepackage{tkz-berge}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\definecolor{shadecolor}{rgb}{0.01,0.199,0.1}

\newtheorem{theorem}{Theorem}

@@

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
   Multicuts rule.
\end{abstract}
\section{Introduction}

  Nunez-Iglesias \etal describe the multicut as
  \say{one-shot agglomeration of supervoxels} whose 
  main drawback is the scalability \cite{nunez_iglesias_2013}.
  Within this work we will overcome the scalability issues.

>>>>

% Include other packages here, before hyperref.
\usepackage{my_macros}
\usepackage{paralist}
\usepackage{amsthm}
\usepackage{dirtytalk}
%\usepackage{framed}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{algpseudocode}
\usepackage{setspace}
%for tikz
\usepackage{tikz,pgfplots}
\usetikzlibrary{arrows,positioning,automata,shadows,fit,shapes}
\usetikzlibrary{arrows,petri,topaths}
\usetikzlibrary{positioning,fit,calc}
\usetikzlibrary{shapes.arrows,chains,decorations.pathreplacing,fadings}
\usepackage{tkz-berge}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\definecolor{shadecolor}{rgb}{0.01,0.199,0.1}
\usepackage{xargs} 
\newtheorem{theorem}{Theorem}

@@

\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
\newcommandx{\unsure}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}
\newcommandx{\change}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}
\newcommandx{\info}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}}
\newcommandx{\improvement}[2][1=]{\todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}}
\newcommandx{\thiswillnotshow}[2][1=]{\todo[disable,#1]{#2}}

@@

\listoftodos[Notes]
%%%%%%%%% ABSTRACT
\begin{abstract}
   We address the problem of partitioning a  graph
   into a previously unknown number of clusters.
   Among all partitions, the one with the minimal 
   sum of of cut edge weights is chosen. 
   This problem is known as correlation clustering 
   or multicut.
   We propose a general framework to find
   high quality approximate solutions for 
   this NP-hard problem based on a move making algorithm:
   We use candidate solutions from a proposal generator
   to iteratively improve the best observed solution similar
   to fusion moves.
   The proposed solver outperforms any other solver
   w.r.t. to any time performance.
   The solutions found by this solver are close
   to global optimal solutions w.r.t. energy
   and problem specific measurements as VI for
   image segmentation problems.

\end{abstract}
\section{Introduction}

\todo[inline]{should there be a general introduction to multicuts?}

Nunez-Iglesias \etal describe the multicut as
\say{one-shot agglomeration of supervoxels} whose 
main drawback is the scalability \cite{nunez_iglesias_2013}.
To address scalability, supernodes can be useful.
To create supernodes, some edges will be contracted
and their nodes are merged into super-nodes.
Doing so, we can reduce  the graph 
to a reasonable size, such that we can find
global optimal multicut solutions within reasonable time.
%
Any edge which is contracted is lost.
If such an edge is cut in the global optimal solution, we cannot 
find this global optimal solutions.
Therefore we avoid fixed decisions and use a
dynamic energy aware contraction scheme.
%
Different edge contractions lead to different super-node graphs.
A trivial approach is the following.
Create different super-node graphs, optimize them with multicuts,
and take the result which leads to the lowest energy
on the unmodified initial graph.
% 
Doing so, we throw away all results which do not have the lowest energy.
Within this work we propose a framework which 
combine multiple \emph{proposal} super-node graphs
without any premature irreversible decisions.
Furthermore, multiple super-node graphs are combined such
that the information form all of them is used.
\todo[inline]{\emph{proposal} super-node graphs sounds shitty}
